Taking uncertainty in word embedding bias estimation seriously: a  bayesian

### 2022-07-28 paperDraft/paperDraft6.Rmd

weat1Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_google.csv")[,-1])
precisWeat1Google <- readRDS("resultsDFs/Weat1GoogleDF.rds")
resultsWeat1Google <- plotFromPrecis(precis = precisWeat1Google,
                                     dataset = weat1Google,
                                     list = "Weat 1",
                                     embedding = "Google",
                                     ylims = c(.8,1.05))

weat1Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_glove.csv")[,-1])
precisWeat1Glove <- readRDS("resultsDFs/Weat1GloveDF.rds")
resultsWeat1Glove <- plotFromPrecis(precis = precisWeat1Glove,
                                     dataset = weat1Glove,
                                     list = "Weat 1",
                                     embedding = "Glove",
                                     ylims = c(.75,1.2))

weat1Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_reddit.csv")[,-1])
precisWeat1Reddit <- readRDS("resultsDFs/Weat1RedditDF.rds")
resultsWeat1Reddit <- plotFromPrecis(precis = precisWeat1Reddit,
                                     dataset = weat1Reddit,
                                     list = "Weat 1",
                                     embedding = "Reddit",
                                      ylims = c(.5,1.1))

religionGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_google_dataset.csv")[,-1])
precisReligionGoogle <- readRDS("resultsDFs/ReligionGoogleDF.rds")
resultsReligionGoogle <- plotFromPrecis(precis = precisReligionGoogle,
                                     dataset = religionGoogle,
                                     list = "Religion",
                                     embedding = "Google",
                                      ylims = c(.65,1.05))

religionGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_glove_dataset.csv")[,-1])
precisReligionGlove <- readRDS("resultsDFs/ReligionGloveDF.rds")
resultsReligionGlove <- plotFromPrecis(precis = precisReligionGlove,
                                        dataset = religionGlove,
                                        list = "Religion",
                                        embedding = "Glove",
                                        ylims = c(.7,1.1))

@@

raceGoogle <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_google_dataset.csv")[,-1])
precisRaceGoogle <- readRDS("resultsDFs/RaceGoogleDF.rds")
resultsRaceGoogle <- plotFromPrecis(precis = precisRaceGoogle,
                                        dataset = raceGoogle,
                                        list = "Race",
                                        embedding = "Google",
                                     ylims = c(.8,1.1))

raceGlove <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_glove_dataset.csv")[,-1])
precisRaceGlove <- readRDS("resultsDFs/RaceGloveDF.rds")
resultsRaceGlove <- plotFromPrecis(precis = precisRaceGlove,
                                    dataset = raceGlove,
                                    list = "Race",
                                    embedding = "Glove",
                                    ylims = c(.7,1.1))

@@

genderGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_google_dataset.csv")[,-1])
precisGenderGoogle <- readRDS("resultsDFs/GenderGoogleDF.rds")
resultsGenderGoogle <- plotFromPrecis(precis = precisGenderGoogle,
                                    dataset = genderGoogle,
                                    list = "Gender",
                                    embedding = "Google",
                                     ylims = c(.6,1.05))

genderGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_glove_dataset.csv")[,-1])
precisGenderGlove <- readRDS("resultsDFs/GenderGloveDF.rds")
resultsGenderGlove <- plotFromPrecis(precis = precisGenderGlove,
                                      dataset = genderGlove,
                                      list = "Gender",
                                      embedding = "Glove",
                                      ylims = c(.5,1.1))

@@

resultsGenderReddit <- plotFromPrecis(precis = precisGenderReddit,
                                     dataset = genderReddit,
                                     list = "Gender",
                                     embedding = "Reddit",  ylims = c(.4,1.1))

>>>>

weat1Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_google.csv")[,-1])
precisWeat1Google <- readRDS("resultsDFs/Weat1GoogleDF.rds")
resultsWeat1Google <- plotFromPrecis(precis = precisWeat1Google,
                                     dataset = weat1Google,
                                     list = "Weat 1",
                                     embedding = "Google")

weat1Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_glove.csv")[,-1])
precisWeat1Glove <- readRDS("resultsDFs/Weat1GloveDF.rds")
resultsWeat1Glove <- plotFromPrecis(precis = precisWeat1Glove,
                                     dataset = weat1Glove,
                                     list = "Weat 1",
                                     embedding = "Glove")

weat1Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_reddit.csv")[,-1])
precisWeat1Reddit <- readRDS("resultsDFs/Weat1RedditDF.rds")
resultsWeat1Reddit <- plotFromPrecis(precis = precisWeat1Reddit,
                                     dataset = weat1Reddit,
                                     list = "Weat 1",
                                     embedding = "Reddit")

religionGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_google_dataset.csv")[,-1])
precisReligionGoogle <- readRDS("resultsDFs/ReligionGoogleDF.rds")
resultsReligionGoogle <- plotFromPrecis(precis = precisReligionGoogle,
                                     dataset = religionGoogle,
                                     list = "Religion",
                                     embedding = "Google")

religionGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_glove_dataset.csv")[,-1])
precisReligionGlove <- readRDS("resultsDFs/ReligionGloveDF.rds")
resultsReligionGlove <- plotFromPrecis(precis = precisReligionGlove,
                                        dataset = religionGlove,
                                        list = "Religion",
                                        embedding = "Glove")

@@

raceGoogle <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_google_dataset.csv")[,-1])
precisRaceGoogle <- readRDS("resultsDFs/RaceGoogleDF.rds")
resultsRaceGoogle <- plotFromPrecis(precis = precisRaceGoogle,
                                        dataset = raceGoogle,
                                        list = "Race",
                                        embedding = "Google")

raceGlove <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_glove_dataset.csv")[,-1])
precisRaceGlove <- readRDS("resultsDFs/RaceGloveDF.rds")
resultsRaceGlove <- plotFromPrecis(precis = precisRaceGlove,
                                    dataset = raceGlove,
                                    list = "Race",
                                    embedding = "Glove")

@@

genderGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_google_dataset.csv")[,-1])
precisGenderGoogle <- readRDS("resultsDFs/GenderGoogleDF.rds")
resultsGenderGoogle <- plotFromPrecis(precis = precisGenderGoogle,
                                    dataset = genderGoogle,
                                    list = "Gender",
                                    embedding = "Google")

genderGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_glove_dataset.csv")[,-1])
precisGenderGlove <- readRDS("resultsDFs/GenderGloveDF.rds")
resultsGenderGlove <- plotFromPrecis(precis = precisGenderGlove,
                                      dataset = genderGlove,
                                      list = "Gender",
                                      embedding = "Glove")

@@

resultsGenderReddit <- plotFromPrecis(precis = precisGenderReddit,
                                     dataset = genderReddit,
                                     list = "Gender",
                                     embedding = "Reddit",  ylims = c(.4,1.2))
